A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-13 PPSN2016/paper.Rnw
Comment
cache

The architecture of the {\sf NodIO} system is divided in two tiers:\begin{enumerate}
\item A REST (representational state transfer) server that responds to
  HTTP requests made by the browsers. These HTTP requests use JSON for
  encoding information, in this case chromosomes and associates
  information send by the clients and return requests made by the
  server.  The server has the capability to
  run a single experiment, storing the incoming chromosomes in a data structure
  that is reset when the solution is found. This data has a finite
  size that erases the oldest chromosomes once it has filled to
  capacity.  
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays the fitness and
  other graphs, some
  additional links, and information on the experiment. This code runs
  an evolutionary algorithm {\em island} that starts with a random
  population, then after every 100 generations, it sends the best individual
  back to the server (via a {\tt PUT} request), and then requests a random
  individual back from the server (via a {\tt GET} request). We have
  kept the number of generations between migrations fixed since it is
  a way of finding out how much real work every client is doing. In
  the version of the server used in this paper, we implemented a
  policy by which the combination IP-fitness value could only be
  inserted once into the cache. That means that if a particular IP
  sends the fitness 99 into the server, it will be accepted only
  once. The main intention of this policy was to avoid {\em
    overlapping} of contributions, with clients still running an {\em
    old} run of the experiment contributing after a new one had
  started. This did not completely avoid these contributions: if the
  clients of the {\em old} run increased their new fitness, it would
  still be allowed. 
\end{enumerate}

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different web technologies, such as JQuery or {\tt
  Chart.js} have been used to build the user interface elements of the
framework, which should be running in
\url{http://nodio-jmerelo.rhcloud.com}, a free resource hosted in the
OpenShift Platform as a Service.\footnote{It is not guaranteed to be running,
or running the same version, when you read this, however; you can always get
the sources from GitHub and set it up yourself.}
%
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the proposed system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}

@@

For every new individual sent by the clients to the cache, several
pieces of meta data were stored: a time stamp, the client IP, the chromosome and
value, the cache size in that particular moment, and also if that
individual actually updated the cache or not.

>>>>

The architecture of the {\sf NodIO} system is divided in two tiers:\begin{enumerate}
\item A REST (representational state transfer) server that responds to
  HTTP requests made by the browsers. These HTTP requests use JSON for
  encoding information, in this case chromosomes and associates
  information send by the clients and return requests made by the
  server.  The server has the capability to
  run a single experiment, storing the incoming chromosomes in a cache data structure
  that is reset when the solution is found. This data has a finite
  size that erases the oldest chromosomes once it has filled to
  capacity.  
\item A client that includes the evolutionary algorithm as
  JavaScript code embedded in a web page that displays the fitness and
  other graphs, some
  additional links, and information on the experiment. This code runs
  an evolutionary algorithm {\em island} that starts with a random
  population, then after every 100 generations, it sends the best individual
  back to the server (via a {\tt PUT} request), and then requests a random
  individual back from the server (via a {\tt GET} request). We have
  kept the number of generations between migrations fixed since it is
  a way of finding out how much real work every client is doing. In
  the version of the server used in this paper, we implemented a
  policy by which the combination IP-fitness value could only be
  inserted once into the cache. That means that if a particular IP
  sends the fitness 99 into the server, it will be accepted only
  once. The main intention of this policy was to avoid {\em
    overlapping} of contributions, with clients still running an {\em
    old} run of the experiment contributing after a new one had
  started. This did not completely avoid these contributions: if the
  clients of the {\em old} run increased their new fitness, it would
  still be allowed. 
  % As I remember we kept the run_number so IPs with old runs
  % did not interfere with newer ones. But you are saying: what if they are super slow 
  % and always PUT when the run is already over?, we want to receive 
  % those individuals? 
  % "That means that if a particular IP
  % sends the fitness 99 into the server, it will be accepted only
  % once."  
  % once per run?
  %  but different individuals could have the same fitness, are we limiting the search? 
  %  maybe we could have multiple versions of the pool a la MVCC  :)
  % I think if we are just trying to limit overlapping of the experiments
  % then PUTs should send the run's seq_number and completly remove it.

\end{enumerate}

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different JavaScript libraries, such as JQuery or {\tt
  Chart.js} have been used to build the user interface elements of the
framework, which should be running in
\url{http://nodio-jmerelo.rhcloud.com}, a free resource hosted in the
OpenShift Platform as a Service.\footnote{It is not guaranteed to be running,
or running the same version, when you read this, however; you can always get
the sources from GitHub and set it up yourself.}
%
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the proposed system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}

@@

For every new individual sent by the clients to the cache, several
% We have not presented the "cache",  only the server and
% ..storing the incoming chromosomes in a data structure
% Im changing over there to cache
pieces of meta data were stored: a time stamp, the client IP, the chromosome and
value, the cache size in that particular moment, and also if that
individual actually updated the cache or not.
